A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum sequential games with imcomplete information

### 2015-07-24 paper.tex
cosmetics
wip

\maketitle
\begin{abstract}We present a simple primal-dual algorithm for
  computing approximate Nash equilibria in two-person zero-sum
  sequential games with  imcomplete information and perfect recall
  (like Texas Hold'em Poker). Our algorithm only performs basic
  iterations (i.e iterations involving no calls to external
  first-order oracles, etc.)
  and is applicable to a broad class of two-person zero-sum games
  including simultaneous games and sequential games with imcomplete
  information and perfect recall. The applicability to the latter kind
  of games is thanks to the sequence-form representation
  \cite{koller1992complexity} which allows us to encode any such game
  as a matrix game with polyhedral strategy profiles. We prove that
  the number of iterations needed to produce a Nash equilibrium with a
  given precision is inversely proportional to the desired
  precision. We also present experimental results on simulated and
  real games (Kuhn poker).
\end{abstract}

@@

\subsection{Nash-equilibrium concepts and statement of the problem}
The sequence-form representation for two-person zero-sum games with
imcomplete information was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
established that for such games, there exist sparse matrices
$A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
  n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in
\mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$,
$l_1$, and $l_2$ are all linear in the size of the game tree (number
of states in the game) and such that Nash equilibria correspond to
pairs $(x, y)$ of \textit{realization plans} which solve the primal
LCP (Linear Convex Program)
\begin{equation}
  \begin{aligned}
     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{
       subject to: }(y,p) \in \mathbb{R}^{n_2} \times
     \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

@@

@@

\subsection{Our contribution}
One cannot directly attack the LCPs \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} via a traditional primal-dual algorithm
(for example \cite{chambolle2010,chambolle2014ergodic}) because
computing the euclidean projections $\proj_{Q_k}$ is very difficult
(in fact, such subproblems would have to be solved
iteratively\footnote{An ``exception to the rule'' is the case where
  the $Q_k's$ are simplexes, so that the projections can be computed
  exactly using \cite{duchi2008efficient}.}). Also,
the primal-dual gap might explode even at ``nearly feasible'' points,
leaving a primal-dual algorithm with no clear indication whatsoever,
on whether progress is being made or not. So need to way to
\begin{itemize}
\item[--] avoid having to compute the projections $\proj_{Q_k}$,
\item[--] have control over how far we are from the set of equilibria and
  avoid infinite (and thus non-informative) primal-dual gaps.
\end{itemize}

Developing on an alternative notion of approximate equilibria (see
Definition \ref{thm:cool_notion})
homologuous to that presented in Definition \ref{thm:approx_nash}, we
device a primal-dual algorithm (Algorithm \ref{Tab:algo}) for
computing approximate Nash equilibria in sequential two-person
zero-sum games with imcomplete information and perfect recall. We also
prove (Theorem \ref{thm:pd})
that the number of iterations required by the algorithm to
produce an approximation equilibrium to a precision $\epsilon$ is
$\mathcal{O}(1/\epsilon)$.%%  The source of approximation in our scheme
%% is that we explicitly control how close we are to the feasible set
%% $Q_1 \times Q_2$.

@@

\section{Our contributions}
\subsection{Reformulation as a Generalized Saddle-point Problem (GSP)}
\label{sec:gsp}
In the next theorem, we show that the said LCP problems can be
conveniently written as a \textit{Generalized Saddle-point Problem
  (GSP)} in the sense of \cite{he2013accelerating}.
\begin{theorem}
Define two proper closed convex functions
  \begin{eqnarray}
    \left.
    \begin{aligned}
      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
        i_{y \ge 0} + \langle e_1,p\rangle\\
        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
          i_{x \ge 0} + \langle e_2, q\rangle
    \end{aligned}
    \right\}
    \label{eq:things}
  \end{eqnarray}

@@

\subsection{A more amenable notion of approximate equilibria}
\subsubsection{Interlude: Proximal calculus}
Let us introduce some notions from modern convex analysis which will be
useful in what follows. Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by
\begin{eqnarray}
  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
    otherwise.}
\end{eqnarray}
At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
etc.). Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
  convex function. The \textit{effective domain} of $f$, denoted
  $dom(f)$, is defined as
\begin{eqnarray}
  dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subgradient} of $f$ is the set-valued function
\begin{eqnarray}
\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
z \in \mathbb{R}^n\}.
\end{eqnarray}
Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
in case $f$ is differentiable at $x$. If $f$ is convex, its
\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
\rightarrow \mathbb{R}^n$ defined by
\begin{eqnarray}
  \prox_f(x): = \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + f(z).
\end{eqnarray}
For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
operators generalize orthogonal projectors. For example
$\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
(z)_+$. One also has the useful characterization
\begin{eqnarray}
  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
\end{eqnarray}

@@

\subsubsection{Yet another notion of approximate equilibrium}
Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
$\epsilon$-subgradient, for short) of $f$ is the set-valued function
\begin{eqnarray}
\partial_\epsilon f: \mathbb{R}^n \rightarrow
2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto \{s \in \mathbb{R}^n | f(z)
\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
\mathbb{R}^n\}.
\end{eqnarray}

@@

Such a vector $v^*$ is called a Nash $(\epsilon_1, \epsilon_2)$-residual at $(x^*,
y^*, x^*, q^*)$.
\label{thm:cool_notion}
\end{definition}

@@

\subsection{The proposed primal-dual algorithm}
\label{sec:algo}
We now derive and establish the theoretical properties of the
algorithm which is the main object of this manuscript.

\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\epsilon,0)$-equilibrium
$({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k
\leftarrow 0$
\While{$\|{v}_{a}^{(k)}\|/k \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$, \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$, \hspace{.5em}$\Delta x^{(k+1)} \leftarrow
x^{(k+1)}-x^{(k)}$
\State $\Delta q^{(k+1)} \leftarrow \lambda (E_2y -
e_2)$, \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} + \Delta q^{(k+1)}$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
+ E_2^T\Delta q^{(k+1)})$, \hspace{.5em}$\Delta y^{(k+1)} \leftarrow
y^{(k+1)}-y^{(k)}$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$,
\hspace{.5em} $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} +
\frac{1}{\lambda}(\Delta
y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

\subsection{Practical considerations}
\paragraph{\textbf{Efficient computation of $Ay$ and $A^Tx$.}}
In Algorithms \ref{Tab:algo} most of the time is spent
pre-multiplying vectors by $A$ and $A^T$. For \textit{flop-type} poker
games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
$A$ (and thus $A^T$ too)  is very big (up $10^{100}$ rows and columns!)
but has a rich block-diagnoal structure which can be carefully
exploited, as was done in \cite{hoda2010smoothing}. For the purpose of
completeness, we explain the details of the tricks used in
\cite{hoda2010smoothing} for speeding up the computation of these
matvec products.

\begin{definition}(Kronecker product)
Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times
  s}$ be matrices. The kronecker product of $F$ and $B$ is defined by

\begin{equation}
F \otimes B:=\left[
\begin{array}{cccc}
F_{0,0}B & F_{0,1}B & \cdots & F_{0,n-1}B \\
F_{1,0}B & F_{1,1}B & \cdots & F_{1,n-1}B \\
\vdots & \vdots & \ddots & \vdots\\
F_{m-1,0}B & F_{m-1,1}B & \cdots & F_{m-1,n-1}B 
\end{array}\right] \in \mathbb{R}^{mr \times ns}
\end{equation}
\end{definition}

One notes that $(F \otimes B)^T = F^T \otimes B^T$.
$F \otimes B$ can be very much larger than both $F$ and $B$ in
dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
$B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
$10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
\mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
  ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
$s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
easily verfies that $Y$ is the matrix product of the ``small''
matrices $B$, $X$, and $F^T$, i.e

\begin{equation}
  \label{eq:kron_matvec}
  Y = BXF^T
\end{equation}

Now, in Texas Hold'em for example, the payoff matrix $A$ can be
written as block-diagonal matrix whose blocks are sums of Kronecker
products of much smaller sparse matrices as follows

\begin{equation}
  A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2
    \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes
    B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
\label{eq:factor_A}
\end{equation}
See \cite{hoda2010smoothing}. The matrices $F_i$ correspond to
sequences of moves in round $i$ which end in a \textit{fold} action,
and $S$ to the sequences which end in a \textit{showdown}. $B_i$
encodes the betting structure of round $i$, while $W$ encodes the
wind/lose/draw information determined by ranking the players' hands at
showdown. The component matrices $F_i$, $B_i$, $S$, and $W$ are small
enough to be explictly represented whereas it is infeasible to
explicitly represent A. Furthermore, the matrices $F_i$, $B_i$,
$S$, and $W$ are themselves sparse, which allows one to use the
compressed row storage data structure that only stores nonzero entries
(for example \textit{scipy.sparse.csr\_matrix}, in the Python
programming language).

Such a representation of the payoff matrix $A$ trivializes matvec
operations involving $A$ or $A^T$ (thanks to formula
\eqref{eq:kron_matvec} above, applied to their diagonal blocks and
exploiting the sparsity of these blocks themselves). Of course, one
can always write the payoff matrix $A$ of a flop-type Poker game in a
form similary to \eqref{eq:factor_A} by applying appropriate
permutations to the enumeration of the players's sequences.

\paragraph{\textbf{Computing $\|K\|$.}}
Also the 2-norm $\|K\|$ of the linear operator $K$, can be efficiently
computed using the power iteration (Perron-Frobenius).

\section{Experimental results}
\label{sec:results}
To access the practical quality of the proposed algorithm, we
tested it on simulated and real games.
\paragraph{Basic test-bed: Matrix games on simplexes.}
As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
\times 1000$ random matrix whose entries are uniformly identically
distributed in the closed interval $[-1, 1]$. We compared our proposed
Algorithm \ref{Tab:algo} with Nesterov's \cite{nesterov2005a} and Gilpin's et
al. \cite{gilpinfirst}. The results of the benchmarks are shown in
Figure \ref{Tab:dgap_curve}\textit{(a)}...

\begin{figure}[!htpb]
  \subfigure[Matrix game on simplexes]{
    \includegraphics[width=.5\linewidth]{0.pdf}
  }
  %% \hspace{-2em}
  %% \subfigure[Toy Poker]{
  %%   \includegraphics[width=.5\linewidth]{SimplifiedPoker_dgap.pdf}
  %% }
  \hspace{-2em}
  \subfigure[Kuhn 3-card Poker]{
    \includegraphics[width=.5\linewidth]{Kuhn3112_dgap.pdf}
  }
  \vspace{-1em}
  \hspace{-2em}
  \includegraphics[width=.5\linewidth]{1.pdf}
  %% \hspace{-1em}
  %% \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
  \hspace{-1em}
  \includegraphics[width=.5\linewidth]{Kuhn3112_NE.pdf}
  \caption{Convergence curves of Algorithm
    \ref{Tab:algo}. \textbf{Top row}: Evolution of ergodic
    primal-dual gap. \textbf{Bottom row}: Evolution of
    value of game.}
  \label{Tab:dgap_curve}
\end{figure}

>>>>

\maketitle
\begin{abstract}We present a simple primal-dual algorithm for
  computing approximate Nash equilibria in two-person zero-sum
  sequential games with  imcomplete information and perfect recall
  (like Texas Hold'em Poker). Our algorithm only performs basic
  iterations (i.e iterations involving no calls to external
  first-order oracles, etc.)
  and is applicable to a broad class of two-person zero-sum games
  including simultaneous games and sequential games with imcomplete
  information and perfect recall. The applicability to the latter kind
  of games is thanks to the sequence-form representation
  \cite{koller1992complexity} which allows us to encode any such game
  as a matrix game with polyhedral strategy profiles. We prove that
  the number of iterations needed to produce a Nash equilibrium with a
  given precision is inversely proportional to the
  precision. We also present experimental results on simulated and
  real games (Kuhn poker).
\end{abstract}

@@

\subsection{Nash-equilibrium concepts and statement of the problem}
The sequence-form for two-person zero-sum games was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
established that for sequential two-person zero-sum games with
imcomplete information and perfect recall, there exist sparse matrices
$A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
  n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in
\mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$,
$l_1$, and $l_2$ are all linear in the size of the game tree (number
of states in the game) and such that Nash equilibria correspond to
pairs $(x, y)$ of \textit{realization plans} which solve the primal
LCP
\begin{equation}
  \begin{aligned}
     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{
       subject to: }(y,p) \in \mathbb{R}^{n_2} \times
     \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

@@

\paragraph{Our contribution.}
Developing on a homologuous and alternative notion of approximate equilibria
, we device a primal-dual algorithm (Algorithm \ref{Tab:algo}) for
computing approximate Nash equilibria in sequential two-person
zero-sum games with imcomplete information and perfect recall. We also
prove that the number of iterations required by the algorithm to
produce an approximation equilibrium to a precision $\epsilon$ is
$\mathcal{O}(1/\epsilon)$.

@@

@@

\section{Reformulation as a Generalized Saddle-point Problem (GSP)}
\label{sec:gsp}
One cannot directly attack the LCPs \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} via a traditional primal-dual algorithm
(for example \cite{chambolle2010,chambolle2014ergodic}) because
computing the euclidean projections $\proj_{Q_k}$ is very difficult
(in fact, such subproblems would have to be solved
iteratively\footnote{An ``exception to the rule'' is the case where
  the $Q_k's$ are simplexes, so that the projections can be computed
  exactly using \cite{duchi2008efficient}.}). Also,
the primal-dual gap might explode even at ``nearly feasible'' points,
leaving a primal-dual algorithm with no clear on whether progress is
being made or not. So need to way to
\begin{itemize}
\item[--] avoid having to compute the projections $\proj_{Q_k}$,
\item[--] have control over how far we are from the set of equilibria and
  avoid infinite (and thus non-informative) primal-dual gaps.
\end{itemize}

In the next theorem, we show that the said LCP problems can be
conveniently written as a \textit{Generalized Saddle-point Problem
  (GSP)} in the sense of \cite{he2013accelerating}.
\begin{theorem}
Define two proper closed convex functions
  \begin{eqnarray}
    \left.
    \begin{aligned}
      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
        i_{y \ge 0} + \langle e_1,p\rangle\\
        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
          i_{x \ge 0} + \langle e_2, q\rangle
    \end{aligned}
    \right\}
    \label{eq:things}
  \end{eqnarray}

@@

\section{A more amenable notion of approximate equilibrium}
\subsection{Interlude: Proximal calculus}
Let us introduce some notions in modern convex analysis which will be
useful in what follows. Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by
\begin{eqnarray}
  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
    otherwise.}
\end{eqnarray}
At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
etc.). Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
  convex function. The \textit{effective domain} of $f$, denoted
  $dom(f)$, is defined as
\begin{eqnarray}
  dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subgradient} of $f$ is the set-valued function
\begin{eqnarray}
\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
z \in \mathbb{R}^n\}.
\end{eqnarray}
Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
in case $f$ is differentiable at $x$. If $f$ is convex, its
\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
\rightarrow \mathbb{R}^n$ defined by
\begin{eqnarray}
  \prox_f(x): = \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + f(z).
\end{eqnarray}
For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
operators generalize orthogonal projectors. For example
$\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
(z)_+$. One also has the useful characterization
\begin{eqnarray}
  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
\end{eqnarray}

@@

Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
$\epsilon$-subgradient, for short) of $f$ is the set-valued function
\begin{eqnarray}
\partial_\epsilon f: \mathbb{R}^n \rightarrow
2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto \{s \in \mathbb{R}^n | f(z)
\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
\mathbb{R}^n\}.
\end{eqnarray}

@@

Such a vector $v^*$ is called a Nash $\epsilon$-residual at $(x^*,
y^*, x^*, q^*)$.
\label{thm:cool_notion}
\end{definition}

@@

\section{The proposed primal-dual algorithm}
\label{sec:algo}
We now derive and establish the theoretical properties of the
algorithm which is the main object of this manuscript.

\subsection{Algorithm and convergence rate}
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\epsilon,0)$-equilibrium
$({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k
\leftarrow 0$
\While{$\|{v}_{a}^{(k)}\|/k \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$, \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$, \hspace{.5em}$\Delta x^{(k+1)} \leftarrow
x^{(k+1)}-x^{(k)}$
\State $\Delta q^{(k+1)} \leftarrow \lambda (E_2y -
e_2)$, \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} + \Delta q^{(k+1)}$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
+ E_2^T\Delta q^{(k+1)})$, \hspace{.5em}$\Delta y^{(k+1)} \leftarrow
y^{(k+1)}-y^{(k)}$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$,
\hspace{.5em} $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} +
\frac{1}{\lambda}(\Delta
y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

\subsection{Practical considerations}
\paragraph{\textbf{Efficient computation of $Ay$ and $A^Tx$.}}
In Algorithms \ref{Tab:algo} most of the time is spent
pre-multiplying vectors by $A$ and $A^T$. For \textit{flop-type} poker
games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
$A$ (and thus $A^T$ too)  is very big (up $10^{100}$ rows and columns!)
but has a rich block-diagnoal structure which can be carefully
exploited, as was done in \cite{hoda2010smoothing}.

%% \begin{definition}(Kronecker product)
%% Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times
%%   s}$ be matrices. The kronecker product of $F$ and $B$ is defined by

%% \begin{equation}
%% F \otimes B:=\left[
%% \begin{array}{cccc}
%% F_{0,0}B & F_{0,1}B & \cdots & F_{0,n-1}B \\
%% F_{1,0}B & F_{1,1}B & \cdots & F_{1,n-1}B \\
%% \vdots & \vdots & \ddots & \vdots\\
%% F_{m-1,0}B & F_{m-1,1}B & \cdots & F_{m-1,n-1}B 
%% \end{array}\right] \in \mathbb{R}^{mr \times ns}
%% \end{equation}
%% \end{definition}

%% One notes that $(F \otimes B)^T = F^T \otimes B^T$.
%% $F \otimes B$ can be very much larger than both $F$ and $B$ in
%% dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
%% $B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
%% $10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
%% \mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
%% without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
%% rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
%%   ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
%% $s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
%% as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
%% easily verfies that $Y$ is the matrix product of the ``small''
%% matrices $B$, $X$, and $F^T$, i.e

%% \begin{equation}
%%   \label{eq:kron_matvec}
%%   Y = BXF^T
%% \end{equation}

%% Now, in Texas Hold'em for example, the payoff matrix $A$ can be
%% written as block-diagonal matrix whose blocks are sums of Kronecker
%% products of much smaller sparse matrices as follows

%% \begin{equation}
%%   A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2
%%     \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes
%%     B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
%% \label{eq:factor_A}
%% \end{equation}
%% See \cite{hoda2010smoothing}. The matrices $F_i$ correspond to
%% sequences of moves in round $i$ which end in a \textit{fold} action,
%% and $S$ to the sequences which end in a \textit{showdown}. $B_i$
%% encodes the betting structure of round $i$, while $W$ encodes the
%% wind/lose/draw information determined by ranking the players' hands at
%% showdown. The component matrices $F_i$, $B_i$, $S$, and $W$ are small
%% enough to be explictly represented whereas it is infeasible to
%% explicitly represent A. Furthermore, the matrices $F_i$, $B_i$,
%% $S$, and $W$ are themselves sparse, which allows one to use the
%% compressed row storage data structure that only stores nonzero entries
%% (for example \textit{scipy.sparse.csr\_matrix}, in the Python
%% programming language).

%% Such a representation of the payoff matrix $A$ trivializes matvec
%% operations involving $A$ or $A^T$ (thanks to formula
%% \eqref{eq:kron_matvec} above, applied to their diagonal blocks and
%% exploiting the sparsity of these blocks themselves). Of course, one
%% can always write the payoff matrix $A$ of a flop-type Poker game in a
%% form similary to \eqref{eq:factor_A} by applying appropriate
%% permutations to the enumeration of the players's sequences.

\paragraph{\textbf{Computing $\|K\|$.}} Power iteration (Perron-Frobenius)...

\section{Experimental results}
\label{sec:results}
To access the practical quality of the proposed algorithm, we
experimented it on real games.

\subsection{Basic test-bed: Matrix games on simplexes}
As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
\times 1000$ random matrix whose entries are uniformly identically
distributed in the closed interval $[-1, 1]$.

\begin{figure}[!htpb]
  \subfigure[Matrix game on simplexes]{
    \includegraphics[width=.33\linewidth]{0.pdf}
  }
  \hspace{-2em}
  \subfigure[Toy Poker]{
    \includegraphics[width=.33\linewidth]{SimplifiedPoker_dgap.pdf}
  }
  \hspace{-2em}
  \subfigure[Kuhn 3-card Poker]{
    \includegraphics[width=.33\linewidth]{Kuhn3112_dgap.pdf}
  }
  \vspace{-1em}
  \hspace{-1em}
  \includegraphics[width=.34\linewidth]{1.pdf}
  \hspace{-1em}
  \includegraphics[width=.33\linewidth]{SimplifiedPoker_NE.pdf}
  \hspace{-1em}
  \includegraphics[width=.33\linewidth]{Kuhn3112_NE.pdf}
  \caption{Convergence curves of Algorithm
    \ref{Tab:algo}. \textbf{Top row}: Evolution of ergodic
    primal-dual gap. \textbf{Bottom row}: Evolution of
    value of game.}
  \label{Tab:dgap_curve}
\end{figure}

\subsection{Sequential games with imcomplete information}
\paragraph{\textbf{Toy Poker game...}}
%% The sequence-form representation for this Toy Poker game is given by
%% (showing only nonzero entries):\\
